Meta-analysis of the Interoceptive Accuracy Scale

### 2025-02-04 analysis/study2.qmd
Update study2.qmd

# names(df1a)
# names(df1b)
# names(df2)  # BPQ, BVAQ, MAIA, ICQ (?), TAS
# names(df3)  # TAS, BPQ
# names(df4)  # BAQ (?), BPQ, MAIA, BRS (resilience?), PBCS (private bodily consciousness?)
# names(df5)  
# names(df6)  # IATS, SSS, GAD, PHQ2
# names(df7a)  # MAIA, STAI, FFMQ, NEOFFI, CES
# names(df7b)  # MAIA, STAI, BPQ, PHQ15, PHQ9
# names(df7c)  # TAS, BPQ, TAS, ASI, BDI, IASV
# names(df8a)  # EDI, BPQ
# names(df8b)  # TAS, PHQ15, PHQ9
# names(df9)  # BFI, STQ, EQ, ECR, 
# names(df10a)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
# names(df10b)  # BDI, STAI, PHQ4
# names(df10c) # PI, MAIA
# names(df11a) # MAIA, TAS, MFQ(DEP), STAI(ANX)
# names(df11b) 
```

@@

```{r}
names(df2)[str_detect(names(df2), "MAIA")]  
names(df4)[str_detect(names(df4), "MAIA")]  # ?
names(df7a)[str_detect(names(df7a), "MAIA")]  
names(df7b)[str_detect(names(df7b), "maia")] 
names(df10a)[str_detect(names(df10b), "MAIA")]
names(df10c)[str_detect(names(df10c), "MAIA")]
names(df11a)[str_detect(names(df11b), "MAIA")]

data <- rbind(
  data,
  make_cor(df2, vars_intero, with = "MAIA_AttentionReg", component="MAIA")  |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df2, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df2, vars_intero, with = "MAIA_BodyTrusting", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),
  make_cor(df2, vars_intero, with = "MAIA_EmoAwareness", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df2, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df2, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df2, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df2, vars_intero, with = "MAIA_SelfReg", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  # df4
  # df7a
  make_cor(df7a, vars_intero, with = "mAIA_ATTENTION_REGULATION", component="MAIA") |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df7a, vars_intero, with = "MAIA_NOTICING", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df7a, vars_intero, with = "MAIA_NON_DISTRACTING", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df7a, vars_intero, with = "MAIA_NON_DISTRACTING", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df7a, vars_intero, with = "MAIA_NOT_WORRYING", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df7a, vars_intero, with = "MAIA_EMOTIONAL_AWARENESS", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df7a, vars_intero, with = "MAIA_SELF_REGULATION", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df7a, vars_intero, with = "MAIA_BODY_LISTENING", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df7a, vars_intero, with = "MAIA_TRUSTING", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),

@@

@@

@@

```{r}
names(df2)[str_detect(names(df2), "TAS")]
names(df3)[str_starts(names(df3), "TAS")]
names(df7c)[str_starts(names(df7c), "TAS")]
names(df8b)[str_starts(names(df8b), "TAS")]
names(df11a)[str_starts(names(df11a), "TAS")]

data <- rbind(
  data,
  make_cor(df2, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df2, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df2, vars_intero, with = "TAS_EOT", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_DescribingFeelings", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_IdentifyingFeelings", component="Alexithymia") |> 
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_ExternallyOrientedThinking", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_des", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_ident", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_ext", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df8b, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df8b, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df11a, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df11a, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df11a, vars_intero, with = "TAS_EOT", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  # BVAQ
  make_cor(df2, vars_intero, with = "BVAQ_Affective", component="Alexithymia") |>
    mutate(var_Correlate = "Affective (BVAQ)"),
  make_cor(df2, vars_intero, with = "BVAQ_Cognitive", component="Alexithymia") |>
    mutate(var_Correlate = "Cognitive (BVAQ)")
)
```

>>>>

# names(df1a)
# names(df1b)
# names(df2)  #TAS, MAIA, ICQ, BPQ, BVAQ
# names(df3)  # TAS, BPQ
# names(df4)  # BPQ, PBCS (private bodily consciousness?), MAIA, BAQ, BRS
# names(df5)  
# names(df6)  # PHQ2, GAD2, SSS8, IATS
# names(df7a)  # STAIT, MAIA, CES (not reported in the paper), FFMQ, NEOFFI
# names(df7b)  # BPQ, PHQ15, PHQ9, MAIA, STAIT, 
# names(df7c)  # CI01 (not reported in the paper), TAS, BPQ, MAIA, ASI, ICQ 
# names(df8a)  # EDI, BPQ
# names(df8b)  # PHQ9, PHQ15, TAS
# names(df9)  # ECR (Experience in Close Relationship Scale), TEAQ (touch experiences and attitudes questionnaire), STQ, TACSEN, UCLA, BFI, DBIA, BO, EQ
# names(df10a)  # ASQ, BPD, GCBS, IPIP6, LIE, MAIA, PHQ4, PI, PID, SPQ
# names(df10b)  # PHQ4, STAIT5, BDI, MAIA
# names(df10c) # MAIA, PI, 
# names(df11a) # MAIA, TAS, MFQ(DEP), STAI(ANX)
# names(df11b) 
```

@@

```{r}
names(df2)[str_detect(names(df2), "MAIA")]  
names(df4)[str_detect(names(df4), "MAIA")]  # individual items
names(df7a)[str_detect(names(df7a), "MAIA")]  
names(df7b)[str_detect(names(df7b), "maia")] 
names(df7c)[str_detect(names(df7c), "MAIA")]
names(df10a)[str_detect(names(df10a), "MAIA")]
names(df10b)[str_detect(names(df10b), "MAIA2")] # all columns with NA values 
names(df10c)[str_detect(names(df10c), "MAIA")]
names(df11a)[str_detect(names(df11b), "MAIA")]

data <- rbind(
  data,
  make_cor(df2, vars_intero, with = "MAIA_AttentionReg", component="MAIA")  |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df2, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df2, vars_intero, with = "MAIA_BodyTrusting", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),
  make_cor(df2, vars_intero, with = "MAIA_EmoAwareness", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df2, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df2, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df2, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df2, vars_intero, with = "MAIA_SelfReg", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),

  # df4

  # df7a
  make_cor(df7a, vars_intero, with = "mAIA_ATTENTION_REGULATION", component="MAIA") |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df7a, vars_intero, with = "MAIA_NOTICING", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df7a, vars_intero, with = "MAIA_NON_DISTRACTING", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df7a, vars_intero, with = "MAIA_NON_DISTRACTING", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df7a, vars_intero, with = "MAIA_NOT_WORRYING", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df7a, vars_intero, with = "MAIA_EMOTIONAL_AWARENESS", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df7a, vars_intero, with = "MAIA_SELF_REGULATION", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df7a, vars_intero, with = "MAIA_BODY_LISTENING", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df7a, vars_intero, with = "MAIA_TRUSTING", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),

@@

  # df7c
   make_cor(df7c, vars_intero, with = "MAIA_noticing", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df7c, vars_intero, with = "MAIA_notdis", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df7c, vars_intero, with = "MAIA_notwor", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df7c, vars_intero, with = "MAIA_attreg", component="MAIA") |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df7c, vars_intero, with = "MAIA_emoaw", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df7c, vars_intero, with = "MAIA_selfreg", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df7c, vars_intero, with = "MAIA_bodlis", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df7c, vars_intero, with = "MAIA_trust", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),

@@

  #df10b

@@

```{r}
#  only one study assess alexithymia with BVAQ (df2)
names(df2)[str_detect(names(df2), "TAS")]
names(df3)[str_starts(names(df3), "TAS")]
names(df7c)[str_starts(names(df7c), "TAS")]
names(df8b)[str_starts(names(df8b), "TAS")]
names(df11a)[str_starts(names(df11a), "TAS")]

data <- rbind(
  data,

  #df2 
  make_cor(df2, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df2, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df2, vars_intero, with = "TAS_EOT", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),

  #df3 
  make_cor(df3, vars_intero, with = "TAS_DescribingFeelings", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_IdentifyingFeelings", component="Alexithymia") |> 
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_ExternallyOrientedThinking", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_des", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_ident", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_ext", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df8b, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df8b, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df11a, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df11a, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df11a, vars_intero, with = "TAS_EOT", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  # BVAQ
  make_cor(df2, vars_intero, with = "BVAQ_Affective", component="Alexithymia") |>
    mutate(var_Correlate = "Affective (BVAQ)"),
  make_cor(df2, vars_intero, with = "BVAQ_Cognitive", component="Alexithymia") |>
    mutate(var_Correlate = "Cognitive (BVAQ)")
)
```
